### 2017-05-13 paper/evaluation.tex
pass section III

From \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \SubjectsGithubNotTestable{} projects were untestable
because of missing dependencies or incompatible testing environment,
for example, and \SubjectsGithubFlaky{} projects were ``flaky''.
\Jbc{Check if this is ok $\rightarrow$} We executed each project's
test suite for three times to identify projects containing flaky tests
and ignored these tests (\ie, using the \CodeIn{@Ignore} annotation
from JUnit) to avoid introducing noise in our experiments.  Our final
set of subjects consists of \numSubjs{} projects.

>>>>

From \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \SubjectsGithubNotTestable{} projects were untestable
because of missing dependencies or incompatible testing environment.
We also found \SubjectsGithubFlaky{} projects with ``flaky'' tests.
We considered those projects but ignored their tests (using JUnit's
\CodeIn{@Ignore} annotation) as to avoid measurement noise.  To detect
those projects, we executed every test suite for three times.  Our
final set of subjects consists of \numSubjs{} projects.
